Reading Notes

### 2020-08-11 2pd.tex
Sprint edits, comments

In order to protect our precious climate, we need a non-polluting, cost-efficient way to provide electricity.
Harnessing solar energy is an important part of a green energy solution.

@@

But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative.

@@

The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.

@@

By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can <get equilibrated morphologies on multiple length scales more efficiently>.

@@

It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.

\section*{Research Objectives}
<gain insight into the limits of coarse graining>
<create models for new opv compounds>
<create a workflow that will make creating new models more accessible>
<develop new tools that help humans do science>
<use that science to help solve energy crisis???????>
<I don't know where to put this but I want a section on best practices>
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

@@

\subsection*{Molecular Dynamics}

<I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
<md in general>
classical physics
interactions between particles
non bonded/bonded/angles/dihedrals
integrates Newton's equations of motion to update the particle positions.
iterated until thermodynamic equilibrium
sample a thermodynamic ensemble
First MD simulation \cite{Alder1957} system of 108 particles, 200 collisions in one hour on an IBM-704.
Now GPUs 100 millions times faster
<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
protein folding \cite{levitt75}, other biological processes, polymers \cite{Gartner2019a}

>>>>

In order to protect our precious climate, we need a non-polluting, cost-efficient way to provide electricity. %EJ: Nice- we'll mostly avoid adjectives unless they're specifically correct for something, so maybe we'd drop 'precious' here, but motivation good~
Harnessing solar energy is an important part of a green energy solution. %EJ: Why? Green energy percentage breakdown?

@@

But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative. %EJ: Cite.

@@

The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device. %EJ: Getting into some technical details- we may  move this to a background section, but it can also work here.
With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment. %EJ: True- but we gotta make people feel this.

@@

By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can <get equilibrated morphologies on multiple length scales more efficiently>. %EJ: cool
%% One thing that's possibly missing in the motivation right now is a rundown of prior simulation techniques and coarse-graining strategies and where they've fallen short.

@@

It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.

\section*{Research Objectives}
%EJ: Nice. Attempting to reorder based on heirarchy
<use that science to help solve energy crisis???????>
<create models for new opv compounds>
<gain insight into the limits of coarse graining>
<develop new tools that help humans do science>
<create a workflow that will make creating new models more accessible>
<I don't know where to put this but I want a section on best practices>
%EJ: Learning and incorporating best practices might actually be a new facet of your work. Like, we can point to the computational research papers that show how this wasn't done so much in the past, but it's happening better now, and we're going to lean into it- I think it fits.
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

@@

\subsection*{Molecular Dynamics}
%EJ: Here or above: Why MD the right tool?
<I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
<md in general>
classical physics
interactions between particles
non bonded/bonded/angles/dihedrals
integrates Newton's equations of motion to update the particle positions.
iterated until thermodynamic equilibrium
sample a thermodynamic ensemble
First MD simulation \cite{Alder1957} system of 108 particles, 200 collisions in one hour on an IBM-704.
Now GPUs 100 millions times faster
<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
protein folding \cite{levitt75}, other biological processes, polymers \cite{Gartner2019a}
